Descriptives

### 2019-09-08 code/sample_descriptives.Rmd
big update

## Load Packages
```{r packages}
library(tidyverse)
library(skimr)
library(formr)
```

## Session Info
```{r session info}
sessionInfo()
```

@@

```{r import data}
main <- read_csv("data/main.csv")

@@

```{r}
main_descriptives_full<- main %>% 
  filter(field_of_study_mc == "Psychology" | study_degree_field == "Psychology") %>% 
  select(age, sex, semester, study_stage_mc, study_stage_open, 
         uni_bachelor, uni_current, study_degree, study_degree_field, 
         study_degree_year, study_degree_yesno, comments, exp_specific)

# Number of included participants.
(n_participants_full <- main_descriptives_full %>% nrow())

# General overview
main_descriptives_full %>% skim()

# Participants' genders
main_descriptives_full %>% pull(sex) %>% table()

# Percentages of participants' genders
(main_descriptives_full %>% pull(sex) %>% table()) / n_participants_full * 100

# Look at age distribution
main_descriptives_full %>% pull(age) %>% hist(main = "Age Histogram", xlab="age")
main_descriptives_full %>% pull(age) %>% table()

# Raw number of participants per semester and study stage
main_descriptives_full %>% 
  filter(study_stage_mc != "Other") %>% 
  filter(semester < 11) %>% 
  mutate(semester = ifelse(semester %% 2 == 0, semester - 1, semester)) %>% 
  mutate(semester = factor(semester, 
                           labels = c("1/2", "3/4", "5/6", "7/8", "9/10"))) %>% 
  group_by(semester, study_stage_mc) %>% 
  summarise(n = n()) %>% 
  arrange(study_stage_mc)

# Percentages of participants in different study stages
(main_descriptives_full %>% pull(study_stage_mc) %>% 
    table()) / n_participants_full *100
```

@@

```{r}
main_descriptives_filtered <- main %>% 
  filter(field_of_study_mc == "Psychology" | study_degree_field == "Psychology") %>% 
  filter(emp_experience == "Yes") %>% 
  select(age, sex, semester, study_stage_mc, study_stage_open, 
         uni_bachelor, uni_current, study_degree, study_degree_field, 
         study_degree_year, study_degree_yesno, comments, exp_specific)

# Number of included participants.
(n_participants <- main_descriptives_filtered %>% nrow())

# General overview
main_descriptives_filtered %>% skim()

# Participants' genders
main_descriptives_filtered %>% pull(sex) %>% table()

# Percentages of participants' genders
(main_descriptives_filtered %>% pull(sex) %>% table()) / n_participants * 100

# Look at age distribution
main_descriptives_filtered %>% pull(age) %>% hist(main = "Age Histogram", xlab="age")
main_descriptives_filtered %>% pull(age) %>% table()

# Percentages of participants in different study stages
(main_descriptives_filtered %>% pull(study_stage_mc) %>% table()) / n_participants *100

# Raw number of participants per semester and study stage
main_descriptives_filtered %>% 
  filter(study_stage_mc %in% c("Bachelor", "Master")) %>% 
  mutate(semester = ifelse(semester %% 2 == 0, semester - 1, semester)) %>% 
  mutate(semester = ifelse(semester > 10, 11, semester)) %>% 
  mutate(semester = factor(semester, 
                           labels = c("1/2", "3/4", "5/6", "7/8", "9/10", ">10"))) %>% 
  group_by(semester, study_stage_mc) %>% 
  summarise(n = n()) %>% 
  arrange(study_stage_mc)

# Number of Projects
main_descriptives_filtered$exp_specific %contains% "1" %>% sum() # Expra
main_descriptives_filtered$exp_specific %contains% "2" %>% sum() # Project
main_descriptives_filtered$exp_specific %contains% "3" %>% sum() # Bachelor's Thesis
main_descriptives_filtered$exp_specific %contains% "4" %>% sum() # Master's Thesis
main_descriptives_filtered$exp_specific %contains% "5" %>% sum() # Other
```

>>>>

@@

```{r import data}
wide <- read_csv("data/wide.csv")

@@

```{r}
wide_descriptives_full<- wide %>% 
  filter(field_of_study_mc == "Psychology" | study_degree_field == "Psychology") %>% 
  select(age, sex, semester, study_stage_mc, study_stage_open, 
         uni_bachelor, uni_current, study_degree, study_degree_field, 
         study_degree_year, study_degree_yesno, comments, exp_specific)

# Number of included participants.
(n_participants_full <- wide_descriptives_full %>% nrow())

# General overview
wide_descriptives_full %>% skim()

# Participants' genders
wide_descriptives_full %>% pull(sex) %>% table()

# Percentages of participants' genders
(wide_descriptives_full %>% pull(sex) %>% table()) / n_participants_full * 100

# Look at age distribution
wide_descriptives_full %>% pull(age) %>% hist(main = "Age Histogram", xlab="age")
wide_descriptives_full %>% pull(age) %>% table()

# Raw number of participants per semester and study stage
wide_descriptives_full %>% 
  filter(study_stage_mc != "Other") %>% 
  filter(semester < 11) %>% 
  mutate(semester = ifelse(semester %% 2 == 0, semester - 1, semester)) %>% 
  mutate(semester = factor(semester, 
                           labels = c("1/2", "3/4", "5/6", "7/8", "9/10"))) %>% 
  group_by(semester, study_stage_mc) %>% 
  summarise(n = n()) %>% 
  arrange(study_stage_mc)

# Percentages of participants in different study stages
(wide_descriptives_full %>% pull(study_stage_mc) %>% 
    table()) / n_participants_full *100
```

@@

```{r}
wide_descriptives_filtered <- wide %>% 
  filter(field_of_study_mc == "Psychology" | study_degree_field == "Psychology") %>% 
  filter(emp_experience == "Yes") %>% 
  select(age, sex, semester, study_stage_mc, study_stage_open, 
         uni_bachelor, uni_current, study_degree, study_degree_field, 
         study_degree_year, study_degree_yesno, comments, exp_specific)

# Number of included participants.
(n_participants <- wide_descriptives_filtered %>% nrow())

# General overview
wide_descriptives_filtered %>% skim()

# Participants' genders
wide_descriptives_filtered %>% pull(sex) %>% table()

# Percentages of participants' genders
(wide_descriptives_filtered %>% pull(sex) %>% table()) / n_participants * 100

# Look at age distribution
wide_descriptives_filtered %>% pull(age) %>% hist(main = "Age Histogram", xlab="age")
wide_descriptives_filtered %>% pull(age) %>% table()

# Percentages of participants in different study stages
(wide_descriptives_filtered %>% pull(study_stage_mc) %>% table()) / n_participants *100

# Raw number of participants per semester and study stage
wide_descriptives_filtered %>% 
  filter(study_stage_mc %in% c("Bachelor", "Master")) %>% 
  mutate(semester = ifelse(semester %% 2 == 0, semester - 1, semester)) %>% 
  mutate(semester = ifelse(semester > 10, 11, semester)) %>% 
  mutate(semester = factor(semester, 
                           labels = c("1/2", "3/4", "5/6", "7/8", "9/10", ">10"))) %>% 
  group_by(semester, study_stage_mc) %>% 
  summarise(n = n()) %>% 
  arrange(study_stage_mc)

# Number of Projects
wide_descriptives_filtered$exp_specific %contains% "1" %>% sum() # Expra
wide_descriptives_filtered$exp_specific %contains% "2" %>% sum() # Project
wide_descriptives_filtered$exp_specific %contains% "3" %>% sum() # Bachelor's Thesis
wide_descriptives_filtered$exp_specific %contains% "4" %>% sum() # Master's Thesis
wide_descriptives_filtered$exp_specific %contains% "5" %>% sum() # Other
```
